Social Visual Analytics: DevOps for Data Scientists

### 2015-03-20 conclusion.tex
fixed up conclusions

We presented a case for a data analytics environment that
supports the visual analytics process, from data acquisition
and exploratory data analysis, through development and deployment.
Building on the extensive previous work on requirements for
visual analytics systems, we designed and deployed a prototype
environment, RCloud.  RCloud supports collaboration and communication
through shared experimental workbooks with version
control, searching, recommending, annotating, and publishing
experiments as web sites and as reusable services.

Our purpose was to gain experience and insight by implementing and
deploying a prototype with a community of working data scientists.
Experience with the RCloud prototype provides evidence that data
science teams and the organizations in which they work benefit from
having capabilities that support the broad visual analytics process.

>>>>

We presented a case for a data analytics environment that
supports the visual analytics process for work by teams.
This inclides data acquisition, exploratory data analysis,
code development and deployment.

Building on previous work that defines requirements for
visual analytics, we designed a prototype environment, RCloud.
RCloud supports collaboration and communication
through shared experimental workbooks with version
control, searching, recommending, annotating, and publishing
experiments as web sites and as reusable services.

We deployed RCloud in a community of working data scientists.
Experience with the RCloud prototype provides evidence that data
science teams and the organizations in which they work benefit from
having capabilities that support collaboration and integrate
the entire visual analytics process.
